Copy number inference with InferCNV

### 2024-06-05 analyses/cell-type-ewings/template_notebooks/04-infercnv.Rmd
remaining spelling
use CNVs

Those cells in grey (bottom left) are cells used as a reference. 
If we were to use total CNVs we would need some sort of cut off for the number. 
Let's look at the distribution of total CNVs to see if we can identify a cut off.

@@

We will call any tumor cell as those with a total number of cnvs greater than the mean(number of cnvs).

>>>>

Those cells in gray (bottom left) are cells used as a reference. 
If we were to use total CNVs we would need some sort of cut off for the number. 
Let's look at the distribution of total CNVs to see if we can identify a cut off.

@@

We will call any tumor cell as those with a total number of CNVs greater than the mean(number of CNVs).
